---
title             : "Measures and Descriptive Stats"
shorttitle        : "Title"

author: 
  - name          : "Vivian Almaraz"
    affiliation   : "1"
  - name          : "AJ Haller"
    affiliation   : "1"
  - name          : "Alejandra Munoz"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Smith College"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "dsc_references.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Method

# Measures

**Relationship satisfaction.** The relationship satisfaction variable is measured with the Relationship Questionnaire (@braiker1979conflict).  10 out of the 30 items in the relationship questionnaire were used to describe aspects of feelings of love within the relationship. The love scale in the relationship questionnaire reflects the degree to which partners within a relationship express concern, feel a sense of belonging, attachment, and closeness. Some items of this scale include “To what extent did you love your partner at this stage?” “How committed do you feel towards your partner?” “How much do you feel you gave to the relationship?.” This was measured on a scale from 1- not at all to 9- very much. This scale was reliable, with a Cronbach's alpha of 0.93. The intraclass correlation coefficient for relationship satisfaction was significant, ICC = 0.698.

**Objectification.** Both self and other objectification was measured with the Self-Objectification Questionnaire (@noll1998mediational). Each participant completed the questionnaire two times, first based on how they would objectify themselves, and then how they objectify their  partner. The Self-Objectification Questionnaire asks participants to rank the extent to which they perceive their bodies by appearance, and by physical ability. Some of these items include weight, physical attractiveness, overall health, and strength. Participants rank these ten aspects from 10 being most important, to 1 being least important. The intraclass correlation coefficient for self objectification is low, ICC = 0.241, and the intraclass correlation coefficient for other objectification is also low, ICC = 0.181. The self and other objectification scales are ranked, and vary for every participant, so we do not expect the intraclass coefficients to be highly correlated.

# Participant Demographics

Our sample started off with 182 couples (N=364). We decided to focus our study on heterosexual couples, leading us to exclude 9 same-sex couples from the sample, leaving us with 173 heterosexual couples (N=346). In our study, we asked the couples to answer questions about the role objectification had in their relationship and about their satisfaction within their relationship. All participants were over the age of 18 and in cohabitation with their partners. The participants were asked to complete questionnaires and a daily measure for 14 days. Participants were not compensated for completing the questionnaires but received $2 for every day they completed the daily measures. The majority (75%) of the participants identified as White, 10% were Asian, 6% were Black, and 5% were Hispanic. Other races accounted for the remaining 3%.  The participants’ ages varied from 26 years of age to 74, with the participants being on average 45.8 years old (sd=8 years).

\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
