---
title             : "Results"
shorttitle        : "Results"

author: 
  - name          : "Vivian Almaraz"
    affiliation   : "1"
  - name          : "AJ Haller"
    affiliation   : "1"
  - name          : "Alejandra Munoz"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Smith College"

bibliography      : ["r-references.bib"]
floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : no
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed)
```

# Results

## Relationship Satisfaction and Partner Objectifcation

Figure 1 shows the direct association between predictors other objectification of a man and the woman's other objectification, and woman’s relationship satisfaction and the relationship satisfaction of the man as the response variable. Figure 1 shows there were no significant associations between a man's objectification of his partner with the woman's relationship satisfaction in romantic relationships (<em>b</em> = 0.011, <em>p</em> = 0.846), and between the woman's objectification of her partner with the man’s relationship satisfaction in romantic relationship (<em>b</em> = 0.002, <em>p</em> = 0.967) (see Figure 1.). Hypothesis 1 is not supported as the results show there is not a statistically significant relationship between other objectification and relationship satisfaction for both men and women. Hypothesis 2 is not supported as the results show there are not statistically significant differences in other objectification and relationship satisfaction between gender. Please refer to table 1 for supplemental information.

## Relationship Satisfaction with Mediation

Models 1 and 2 includes the variable self objectification for both the man and the woman as a mediator between the other objectification of a man with the woman’s relationship satisfaction (model 1), and the associations between other objectification of a woman with the man’s relationship satisfaction (model 2).

In Model 1, there is not a significant association between the man’s partner objectification towards the woman with the woman’s relationship satisfaction while mediating for the woman’s objectification of herself (<em>b</em> = 0.039, <em>p</em> = 0.519)(see Figure 1.).  This does not support our third hypothesis which suggested that the association between man’s objectification of his partner and the partner’s relationship satisfaction is dependent on a woman’s objectification of herself.  However, model 1 did result in a statistically significant association between the man’s partner objectification and the woman’s self objectification (<em>b</em> = 0.279, <em>p</em> = 0.0002)(see Figure 1.). This suggests that a man who objectifies the woman in a heterosexual relationship is associated with the woman objectifying herself more. 

Model 2 shows that there is no significant association between a woman’s objectification of her partner and the partner’s relationship satisfaction with the man’s self objectification as a mediating variable (<em>b</em> = 0.026, <em>p</em> = 0.687)( see Figure 1.).  This does not support our fourth hypothesis that the association between a woman's objectification of her partner and the partner’s relationship satisfaction is dependent on a man’s objectification of himself. However, Model 2 also shows that there is a statistically significant indirect relationship between the woman’s partner objectification and the man’s self objectification (<em>b</em> = 0.209, <em>p</em> = 0.011). This suggests that a woman’s partner objectification towards the man makes men in heterosexual relationships objectify themselves more. Results in model 2 also show that a man’s objectification of himself is associated with a decrease in his relationship satisfaction (<em>b</em> = -0.150, <em>p</em> = 0.015)(see Figure 1.). 

![The Moderated Mediation Model: This figure shows the associations between predictors, mediators, and response variables as the moderated mediation model. Model 1 is represented by green arrows, and model 2 is represented by blue arrows.  Dashed arrows are statistically insignificant coefficients (B) demonstrating p values > 0.05. Bold arrows and asterix are statistically significant coefficients (B) with p values < 0.05.](Images/hypothesis_model_results.png)


<div id="refs" custom-style="Bibliography"></div>
\endgroup
