---
title: "Results Analyses"
author: "Vivian Almaraz"
date: '2022-04-04'
output: html_document
editor_options: 
  chunk_output_type: inline
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# Loading in the dataset
library(tidyverse)
library(nlme)

pairwise <- read.csv("pairwise2.csv")
```

```{r}
pairwise <- pairwise %>%
  rename(self_object_A = self_object.tavg_A, 
         other_object_A = other_object.tavg_A,
         relation_sat_A = relation_qual.avg_A,
         self_object_P = self_object.tavg_P,
         other_object_P = other_object.tavg_P,
         relation_sat_P = relation_qual.avg_P) %>%
  mutate(gender_AF = ifelse(gender_A == 1, "man", "woman")) %>%
  select(Dyad_ID, partnum, gender_A, gender_AF, self_object_A, other_object_A, relation_sat_A, self_object_P, other_object_P, relation_sat_P)
```

##The Four Baron & Kenny Steps Using Multilevel Modeling

###Step 1: Estimating and testing the total effect (c) of Other Objectification on Relationship Satisfaction (Y)

y ~x fives us c

Value = c

```{r}
apim_stp1 <- gls(relation_sat_A ~ gender_AF + other_object_A:gender_AF + other_object_P:gender_AF - 1, # two intercept model for variables, -1 is to make sure that we have two separate intercepts for husband and wife
                 data = pairwise,
                 correlation = corCompSymm(form=~1|Dyad_ID), 
                 weights = varIdent(form=~1|gender_A), 
                 na.action = na.omit)

summary(apim_stp1)
```

###Step 2: Testing the effects of the Other Objectification (X) on the mediators of Wife and Husband Self Objectification (M).

Is the mediator predicted by x? so now tension is out response variable
M ~ X gives us a

Value = a paths for mediation

```{r}
apim_stp2 <- gls(self_object_A ~ gender_AF + other_object_A:gender_AF + other_object_P:gender_AF - 1,
                 data = pairwise,
                 correlation = corCompSymm(form=~1|Dyad_ID), 
                 weights = varIdent(form=~1|gender_A), 
                 na.action = na.omit)

summary(apim_stp2)
```

###Steps 3 and 4: Testing the effects of the Self Objectification (M) and Other Objectficiation (X) on the Relationship Satisfaction (Y). 

Y ~ X + M gives us bc'
(X gives us c' and M gives us b)

```{r}
apim_stp3 <- gls(relation_sat_A ~ gender_AF + other_object_A:gender_AF + other_object_P:gender_AF 
                 + self_object_A:gender_AF + self_object_P:gender_AF - 1,
                 data = pairwise,
                 correlation = corCompSymm(form=~1|Dyad_ID), 
                 weights = varIdent(form=~1|gender_A), 
                 na.action = na.omit)

summary(apim_stp3)
```


#Testing Indirect Effects Using Multilevel Modeling

##Sobel Test

```{r}

sobel <- function(aval, bval, seA, seB){
  
  ab <- aval*bval
  ab_se <- sqrt(aval^2*seB^2+bval^2*seA^2)
  z <- ab/ab_se
  p <- 2*pnorm(z, lower.tail=FALSE)
  
  return(data.frame(indirect_effect = ab, z_value = z, p_value = p))
   
}
```

```{r}
# mans self & other object A

act_H_a <- coef(summary(apim_stp2))[3,1]
act_H_a_se <- coef(summary(apim_stp2))[3,2]
act_H_b <- coef(summary(apim_stp3))[7,1]
act_H_b_se <- coef(summary(apim_stp3))[7,2]

sobel(act_H_a, act_H_b, act_H_a_se, act_H_b_se)
```

```{r}

# womans self & other object A

act_W_a <- coef(summary(apim_stp2))[4,1]
act_W_a_se <- coef(summary(apim_stp2))[4,2]
act_W_b <- coef(summary(apim_stp3))[8,1]
act_W_b_se <- coef(summary(apim_stp3))[8,2]

sobel(act_W_a, act_W_b, act_W_a_se, act_W_b_se)

```

```{r}
# mans self & other object P

act_H_p <- coef(summary(apim_stp2))[5,1]
act_H_p_se <- coef(summary(apim_stp2))[5,2]
act_H_b_p <- coef(summary(apim_stp3))[9,1]
act_H_b_p_se <- coef(summary(apim_stp3))[9,2]

sobel(act_H_p, act_H_b_p, act_H_p_se, act_H_b_p_se)


```

```{r}
# womans self & other object P 

act_W_p <- coef(summary(apim_stp2))[6,1]
act_W_p_se <- coef(summary(apim_stp2))[6,2]
act_W_b_p <- coef(summary(apim_stp3))[10,1]
act_W_b_p_se <- coef(summary(apim_stp3))[10,2]

sobel(act_W_p, act_W_b_p, act_W_p_se, act_W_b_p_se)

```


##MCMAM (MonteCarlo Method) [Selig & Preacher, 2008](http://www.quantpsy.org/medmc/medmc.htm)

```{r}
#Function that returns mcmc CI. 
mcmamCI <- function(aval, bval, varA, varB, n){

#code (Selig & Preacher, 2008).
  require(MASS)
  
  a=aval
  b=bval
  rep=n
  conf=95
  pest=c(a,b)
  acov <- matrix(c(varA, 0, 0, varB),2,2)

  mcmc <- mvrnorm(rep,pest,acov,empirical=FALSE)

  ab <- mcmc[,1]*mcmc[,2]

  low=(1-conf/100)/2
  upp=((1-conf/100)/2)+(conf/100)

  LL=quantile(ab,low)
  UL=quantile(ab,upp)
  LL=format(LL,digits=3)
  UL=format(UL,digits=3)

  CI <- cbind.data.frame(LL, UL)
  return(CI)

}
```

```{r}
# mans self & other object A

act_H_a <- coef(summary(apim_stp2))[3,1]
act_H_a_se <- coef(summary(apim_stp2))[3,2]
act_H_b <- coef(summary(apim_stp3))[7,1]
act_H_b_se <- coef(summary(apim_stp3))[7,2]

mcmamCI(act_H_a, act_H_b, act_H_a_se^2, act_H_b_se^2, 3000)

```

```{r}

# womans self & other object A

act_W_a <- coef(summary(apim_stp2))[4,1]
act_W_a_se <- coef(summary(apim_stp2))[4,2]
act_W_b <- coef(summary(apim_stp3))[8,1]
act_W_b_se <- coef(summary(apim_stp3))[8,2]

mcmamCI(act_W_a, act_W_b, act_W_a_se^2, act_W_b_se^2, 3000)

```

```{r}
# mans self & other object P

act_H_p <- coef(summary(apim_stp2))[5,1]
act_H_p_se <- coef(summary(apim_stp2))[5,2]
act_H_b_p <- coef(summary(apim_stp3))[9,1]
act_H_b_p_se <- coef(summary(apim_stp3))[9,2]

mcmamCI(act_H_p, act_H_b_p, act_H_p_se^2, act_H_b_p_se^2, 3000)

```

```{r}
# womans self & other object P 

act_W_p <- coef(summary(apim_stp2))[6,1]
act_W_p_se <- coef(summary(apim_stp2))[6,2]
act_W_b_p <- coef(summary(apim_stp3))[10,1]
act_W_b_p_se <- coef(summary(apim_stp3))[10,2]

mcmamCI(act_W_p, act_W_b_p, act_W_p_se^2, act_W_b_p_se^2, 3000)

```
















